---
title: 'MATH 437 HW3'
author: "Drew Remmenga"
output:
  pdf_document: default
  html_notebook: default
---
##1.i. \
$T^{2}(X,\mu) = 1(\bar{X}-\mu)^{T}s(X)(\bar{X} - \mu)$
T squared
##1.ii. \
$\frac{n-1}{n} (\bar{X} - \mu)^{T} \hat\Sigma^{-1}(X) (\bar{X}-\mu)$
##1.iii. \
##1.iii.a. \
$A\bar{X}+a$
$A^{T}\Sigma (X)A$
##1.iii.b. \
$A^{T}S(X)A$
$n (A\bar{X}+a - \mu_{y})^{T} A^{T}S^{-1}(X)A (A\bar{X}+a-\mu_{y})$
##1.iii.c. \
##2.\
$(1-\alpha)*100\%$\
$X \pm Z_{1-\alpha/2}* S/\sqrt{n}$\
$X \pm K S / \sqrt{n}$\
$K= Z_{1-\alpha/2}$\
$\phi (k) = 1- \alpha/2$\
$\alpha = 2 - 2 \phi (k)$\
##3. \
For n = 25 p = 3:
$a^{T} X - 1.809 F^{\alpha}_{3,22} \frac{\sqrt{a^{T}\Sigma a}}{25} \leq a^{T} \mu \leq a^{T} X + 1.809 F^{\alpha}_{3,22} \frac{\sqrt{a^{T}\Sigma a}}{25}$\
For n = 25 p = 2:
$a^{T} X - 1.445 F^{\alpha}_{2,23} \frac{\sqrt{a^{T}\Sigma a}}{25} \leq a^{T} \mu \leq a^{T} X + 1.445 F^{\alpha}_{2,23} \frac{\sqrt{a^{T}\Sigma a}}{25}$\
##4.a.\

```{r}
lizard <- read.csv("~/School/Math437/HW3/lizard.dat", sep="")
xbar = c(mean(lizard$mass),mean(lizard$svl),mean(lizard$hls))
xbar
S=cov(lizard[-1])
S
```
##b. \
$n (\bar{X} - \mu)^{T} S^{-1}(X) (\bar{X}-\mu)$
##c. \
```{r}
mu = c(10,70,140)
t((xbar-(mu)))%*%solve(S)%*%(xbar-(mu))

```
##d. \
```{r}
library(DescTools)
HotellingsT2Test(lizard[-1],mu=mu)
```
##e. \
```{r}
S= cov(lizard[,3:4])
S
```
##f. \
```{r}
bivCI <- function(s, xbar, n, alpha, m)
# returns m (x,y) coordinates of 1-alpha joint confidence ellipse of mean
{
x <- sin(2 * pi * (0 : (m - 1)) / (m - 1)) # m points on a unit circle
y <- cos(2 * pi * (0 : (m - 1)) / (m - 1))
cv <- qchisq(1 - alpha, 2) # chi-squared critical value
cv <- cv / n # value of quadratic form
for (i in 1 : m)
{
pair <- c(x[i], y[i]) # ith (x,y) pair
q <- pair %*% solve(s,pair) # quadratic form
x[i] <- x[i] * sqrt(cv / q) + xbar[1]
y[i] <- y[i] * sqrt(cv / q) + xbar[2]
}
cbind(x, y)
}


biv = lizard[,3:4]
plot(biv, col = "red", pch = 16, cex.lab = 1.5)
lines(bivCI(s = var(biv), xbar = colMeans(biv), n = dim(biv)[1],alpha = .01,
m = 1000),type = "l", col = "blue")
lines(bivCI(s = var(biv), xbar = colMeans(biv), n = dim(biv)[1],alpha = .05,
m = 1000),type = "l", col = "red", lwd = 1)
# Add ‘‘+’’ sign
lines(colMeans(biv)[1], colMeans(biv)[2], pch = 3, cex = .8,type = "p", lwd = 1)
```
##g. \
```{r}

conf=bivCI(s = var(biv), xbar = colMeans(biv), n = dim(biv)[1],alpha = .025,
m = 1000)
t.test(lizard[,3])
t.test(lizard[,4])
min(conf[,1])
max(conf[,1])
min(conf[,2])
max(conf[,2])
```
